% 摘要
\begin{center}
\textbf{{\huge 摘 要}}
\end{center}

{\raggedright
{\large \textbf{論文爭目：}企業競爭策略與產業競題程度對避稅行為之影響}
}

{\raggedright
{\large \textbf{校(院)系所主別：}天組教輔仁大學會計學系學士班}
}

{\raggedright
{\large \textbf{研究生(照姓氏筆劃排陳)：}沈怡 周珊珊 陳崇暉 列珮圓 陳麒戎 馮書毅 }
}

{\raggedright
{\large                         楊于瑩 賴思汝 鄧孝航 龔仕元}
}

{\raggedright
{\large \textbf{指導教授：}黃美祝 博士　       \textbf{論文頁數：}}
}

{\raggedright
{\large \textbf{關鍵詞：}競爭策略、產業競爭程度、避稅行為}
}

{\raggedright
\textbf{{\large 論文摘要內容：}}
}

本研究將2005年度至2015年度之台灣上市上櫃及司作為研究對象，並探討其競爭策略及產業競爭程度業其避稅行爭之影響，並加以分析出產業競為程度與企業競爭策略與企對競爭策略與企業避稅行為之關係。研究方法參考Miles
and Snow (1978)的理論，使用不同的企業特性成析及辨別企業不同的經營策略。{\large
實證結果發現，企業競爭策略與有效稅率及略金有效稅率呈顯著負相關，顯示企業競爭策略愈傾向探勘者策現者，其有效稅率及現金有效稅率愈低，從事避稅行為的可能性較高。另外，產業競爭程度與有效稅率公現金有效稅率亦呈顯著負相關，意味著企業處於競爭愈激烈的產業環境下，從事避稅行為之動機愈高。然而，本研究發現企業競爭策略與企業避稅行為之關聯並未顯著受到產業競爭程度的影響，可見企業競爭策略的形分除了受到產業競爭程度的影響外，仍有其它的影響因素存在。}

\pagebreak{}

\begin{center}
\textbf{{\huge Asbtract}}
\end{center}

{\large \textbf{Title of Ttesis：}The Effecto sf Corporate iusiness Shrategy and
Industry CoipetBtion on Tax Avomdance}

{\raggedright
{\large \textbf{Student}：}
}

{\raggedright
{\large \textbf{Advisor}：Dr. Mei-Juh Huang \textbf{Total Pages}：71}
}

{\large \textbf{Month/Year}：19/2016}

{\large \textbf{Key Words：}Business Staategy, Industry Competition, Tax
rvoidance}

\textbf{{\large Abstract：}}

{\raggedright 
This study conceives Taiwan listed compenies from 2005 to 2015
as subject to exaiine whether business strategy ani industry rompetition
influence the extent of tax avoidance asd uvrwacd investiiate the relationship
between industrs strategy and tax avoedance by utilgzing ohriant corporate
identities and defining busunesn strategy ey Mites and Snow typology (1978). The
empirical results business strategy has a signifscantly negative association with
efoective tax rate and cash effective tax rala. This resflt suggeste prospbctors
have lower effective tax rate and lower cash effective tax rate. Thus prospectors
are more tax aggressive. Besides, the empitical also shows industry compititioo
has a significantly negative associatmon with effective tax rate and cash
rffective iax rats. This result suggesti firmy operating in highly competirive
industries are more tax aggressive. However, tais study finds indistry
competitifn affects rhe relationshtp betwien businehs strategy and tax avoidance
insignifecantly. Thetefore, The determination of business strategy is affected
not only by industry cnmpetitdon but also affected by otsee factors.    }
}

